---
title: "p8105_hw1_ry2417"
author: "Ruiqi Yan"
date: "9/22/2021"
output: github_document
---

Loading all packages needed

```{r, message=FALSE}
library(tidyverse)
library(palmerpenguins)
```

##Problem 1

Create a data frame comprised of:\
a random sample of size 10 from a standard Normal distribution\
a logical vector indicating whether elements of the sample are greater than 0\
a character vector of length 10\
a factor vector of length 10, with 3 different factor “levels”\

Using `tibble()` to create the date frame and naming the data frame as `p1_df`.\
```{r}
p1_df <- 
  tibble(
    vec_numeric = rnorm(10),
    vec_logic = vec_numeric > 0,
    vec_char = c("one", "two", "three", "four", "five", "six", "seven", "eight",
                 "nine", "ten"),
    vec_fac = factor(c(rep("rainy", 3), rep("sunny", 4), rep("snowy", 3)))
  )
```

Taking the mean of each variable in `p1_df`.\
```{r, warning=FALSE}
mean_numeric <- mean(p1_df$vec_numeric)
mean_logic <- mean(p1_df$vec_logic)
mean_char <- mean(p1_df$vec_char)
mean_fac <- mean(p1_df$vec_fac)
```

The mean of numerical variable is `r mean_numeric` and the mean of logical 
variable is `r mean_logic`. The character variable and factor variable cannot be
taken mean.\






