---
title: "p8105_hw1_ry2417"
author: "Ruiqi Yan"
date: "9/22/2021"
output: github_document
---

Loading all packages needed

```{r, message=FALSE}
library(tidyverse)
library(palmerpenguins)
```

#Problem 1#

Create a data frame comprised of:\
a random sample of size 10 from a standard Normal distribution\
a logical vector indicating whether elements of the sample are greater than 0\
a character vector of length 10\
a factor vector of length 10, with 3 different factor “levels”\

Using `tibble()` to create the date frame and naming the data frame as `p1_df`.\
```{r}
p1_df <- 
  tibble(
    vec_numeric = rnorm(10),
    vec_logic = vec_numeric > 0,
    vec_char = c("one", "two", "three", "four", "five", "six", "seven", "eight",
                 "nine", "ten"),
    vec_fac = factor(c(rep("rainy", 3), rep("sunny", 4), rep("snowy", 3)))
  )
```

Taking the mean of each variable in `p1_df`.\
```{r, warning=FALSE}
mean_numeric <- mean(p1_df$vec_numeric)
mean_logic <- mean(p1_df$vec_logic)
mean_char <- mean(p1_df$vec_char)
mean_fac <- mean(p1_df$vec_fac)
```

The mean of numerical variable is `r mean_numeric` and the mean of logical 
variable is `r mean_logic`. The character variable and factor variable cannot be
taken mean.\

Convert the logical, character, and factor variables to numeric variables.\
```{r, eval=FALSE}
as.numeric(p1_df$vec_logic)
as.numeric(p1_df$vec_char)
as.numeric(p1_df$vec_fac)
```

The factor variable and the logical variable can be converted to be numeric, but
the character variable cannot be converted. The logical variable has only two 
outcomes, it was reasonable to convert 1 for TRUE and 0 for FALSE. And the 
factor variable has three levels, so it is reasonable to assign each level with
nature number. However, for character vector which contained many different 
words, it has no clue for value that could be assigned to each element. This 
explained how logical variable is taken mean. 








