---
title: "p8105_hw1_ry2417"
author: "Ruiqi Yan"
date: "9/22/2021"
output: github_document
---

Loading all packages needed\

```{r, message = FALSE}
library(tidyverse)
```

## Problem 1

Create a data frame comprised of:\
a random sample of size 10 from a standard Normal distribution\
a logical vector indicating whether elements of the sample are greater than 0\
a character vector of length 10\
a factor vector of length 10, with 3 different factor “levels”\

Using `tibble()` to create the date frame and naming the data frame as `p1_df`.\

```{r, create_df}
set.seed(1111)
p1_df <- 
  tibble(
    vec_numeric = rnorm(10),
    vec_logic = vec_numeric > 0,
    vec_char = c("one", "two", "three", "four", "five", "six", "seven", "eight",
                 "nine", "ten"),
    vec_fac = factor(c(rep("rainy", 3), rep("sunny", 4), rep("snowy", 3)))
  )
```

Taking the mean of each variable in `p1_df`.\

```{r, warning = FALSE, take_mean}
mean_numeric <- round(mean(pull(p1_df, vec_numeric)), 1)
mean_logic <- mean(pull(p1_df, vec_logic))
```

The mean of numerical variable is `r mean_numeric` and the mean of logical variable is `r round(mean_logic, 1)`. Taking means for character 
variable and factor variable do not work.\

Convert the logical, character, and factor variables to numeric variables.\

```{r, eval = FALSE, convert_var}
as.numeric(pull(p1_df, vec_logic))
as.numeric(pull(p1_df, vec_char))
as.numeric(pull(p1_df, vec_fac))
```

The factor variable and the logical variable can be converted to be numeric, but
the character variable cannot be converted. The logical variable has only two 
outcomes, it was reasonable to convert 1 for TRUE and 0 for FALSE. And the 
factor variable has three levels, so it is reasonable to assign each level with
nature number. However, for character vector which contained many different 
words, it has no clue for value that could be assigned to each element. This 
explained how logical variable is taken mean.\

## Problem 2

Loading the `penguins` data set\

```{r, load_penguins}
data("penguins", package = "palmerpenguins")
```

Converting the `penguins` data set to `tibble` called `p2_df`.\

```{r, copy_df}
p2_df <- as_tibble(penguins)
```

Doing some summaries of the data.\

```{r, some_summaries, echo = FALSE}
max_flipper <- max(pull(p2_df, flipper_length_mm), na.rm = TRUE)
min_flipper <- min(pull(p2_df, flipper_length_mm), na.rm = TRUE)
mean_flipper <- round(mean(pull(p2_df, flipper_length_mm), na.rm = TRUE), 1)
max_bill <- max(pull(p2_df, bill_length_mm), na.rm = TRUE)
min_bill <- min(pull(p2_df, bill_length_mm), na.rm = TRUE)
mean_bill <- round(mean(pull(p2_df, bill_length_mm), na.rm = TRUE), 1)
max_bm <- max(pull(p2_df, body_mass_g), na.rm = TRUE)
min_bm <- min(pull(p2_df, body_mass_g), na.rm = TRUE)
mean_bm <- round(mean(pull(p2_df, body_mass_g), na.rm = TRUE), 1)
```

The size of this data set is  `r nrow(p2_df)` observations with `r ncol(p2_df)` 
variables. The variable names are ``r names(p2_df)``.\
The max flipper length is `r max_flipper` mm, the min is `r min_flipper` mm, and the mean is `r mean_flipper` mm.\
The max bill length is `r max_bill` mm, the min is `r min_bill` mm and the mean 
is `r mean_bill` mm.\
The max body mass is `r max_bm` g and the min is `r min_bm` g and the mean is 
`r mean_bm` g.\
The numbers of penguins of each specie are `r table(pull(p2_df, species))` 
(`r names(table(pull(p2_df, species)))`). The numbers of penguins from each island are `r table(pull(p2_df, island))` (`r names(table(pull(p2_df, island)))`).\
There are `r table(pull(p2_df, sex))[1]` females and `r table(pull(p2_df, sex))[2]` males.\

Make a scatter plot of `flipper_length_mm` (y) vs `bill_length_mm` (x); color points using the `species` variable.\

```{r, bill_vs_flipper_scatterplot}
ggplot(p2_df, aes(x = bill_length_mm, 
                  y = flipper_length_mm, 
                  color = species)) + geom_point(na.rm = TRUE)
```

Export the first scatter plot to the project directory using `ggsave`.\

```{r, save_plot}
ggsave("bill_vs_flipper_scatterplot.pdf", height = 6, width = 8)
```












